The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
hab persp intro

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by resource availability and seasonality
[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
Habitat selection, the disproportionate use of available resources or landscape
features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
[@Mayor_2009]. Social structure and habitat selection are intimately
linked: as individuals must share space to interact, and the distribution of
resources influences group dynamics and home range size [@Webber_2018].
<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
Multilayer networks represent a novel framework for considering the influence of
habitat selection and space use on sociality across scales.

>>>>

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure and habitat selection are intimately
linked: individuals must share space to interact and the distribution of
resources influences group dynamics and home range size [@Webber_2018].
Social structure is influenced by resource availability and seasonality
[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
Habitat selection, the disproportionate use of available resources or landscape
features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
[@Mayor_2009]. Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.

<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
